Cluster Dynamics with HETDEX at z < 0.5 - I: Simulated Performance, Mass Recovery, and Limits to Cosmology

### 2016-05-04 ms.tex
add extra math symbols
first big round of Casey comments

%%%%% AUTHORS - PLACE YOUR OWN PACKAGES HERE %%%%%
%\usepackage{epsf}
\usepackage{color}
\usepackage{graphicx}
\usepackage{amsmath}	% Advanced maths commands
\usepackage{amssymb}	% Extra maths symbols
\usepackage{mathrsfs}
\usepackage{natbib}
%\usepackage[colorlinks,urlcolor=blue,citecolor=blue,linkcolor=blue]{hyperref}
\usepackage{multirow}
\usepackage{etoolbox}

@@

\begin{abstract}
\noindent
The distribution of massive clusters of galaxies depends strongly on the total cosmic mass density, the mass variance, and the dark energy equation of state. As such, measures of galaxy clusters can provide constraints on these parameters and even test models of gravity, but only if observables of clusters can lead to accurate estimates of their total masses. Here, we carry out a study to investigate the ability of a blind spectroscopic survey to recover accurate galaxy cluster masses through their velocity dispersion. We focus on the Hobby Eberly Telescope Dark Energy Experiment (HETDEX), which will employ the new VIRUS integral field unit (IFU) spectrograph, over 420 \degsq\ on the sky with a 1/4.5 fill factor. The instrument covers the blue/optical portion of the spectrum (3500--5500~\AAA), allowing surveys with VIRUS to measure redshifts for a large sample of galaxies out to $z < 0.5$ based on their absorption features or [\ion{O}{ii}] $\lambda$3727 emission (and Lyman-$\alpha$ over $1.9 < z < 3.5$). We use a detailed mock galaxy catalog from a semi-analytic model to simulate surveys observed with VIRUS, including: (1) a blind, HETDEX-like survey with an incomplete but uniform spectroscopic selection function; and (2) IFU surveys that target clusters directly, obtaining spectra of all galaxies in a VIRUS-sized field. For both surveys, we include realistic uncertainties from galaxy magnitude and line-flux limits. We benchmark both surveys against spectroscopic observations with ``perfect" knowledge of galaxy line-of-sight velocities. Using both observing strategies, we produce cluster mass probability density functions $P(M_{200c}|\vec{x})$ of a cluster mass ($M_{200c}$) as a function of an observable parameter or set of observable parameters, $\vec{x}$, where we consider cases of where $\vec{x} = \{\sigma\}$, $=\{\sigma, z\}$, and $=\{\sigma,z, N_{gal}\}$ for velocity dispersion, $\sigma$, redshift, and number of observed galaxies, $N_{gal}$. \editorial{This sentence will summarize how well HETDEX will do, and how that might be improved with targeted observations.}
\end{abstract}

\section{Introduction}
Our ability to perform precision cosmology with clusters of galaxies has reached a critical turning point. The widely accepted $\Lambda$CDM model of cosmology makes explicit predictions about the number and masses of galaxy clusters throughout the universe. However, connecting these predictions to a set of, sufficiently large in size, observed clusters remains a principal problem. Specifically, the largest threat to modern, precision, cluster cosmology is not the identification of large numbers of clusters (the total number of clusters known is only going up) but the accurate recovery of galaxy cluster mass \citeeg{Sehgal2011,Plank2014, Bocquet2015}.

As mass is not a direct observable, a lot of work is underway to characterize galaxy cluster masses with an observable feature of galaxy clusters. The goal is to constrain, as best possible, $P(M|z, X)$ the probability ($P$) that a galaxy cluster of given mass ($M$), located at redshift ($z$) determined using observable parameter ($X$). Generally, cluster mass calibrations fall into two distinct camps, simulation based and direct or statistical calibration.

@@

The second broad camp is the direct calibration of cluster masses. This recipe has two distinct but not always independent tracks. The ``direct'' method uses direct observations of a small set of clusters and then uses known mass estimators, X-ray temperatures and luminosities \citeeg{Mantz2010, Rykoff2014}, cosmic microwave background (CMB) observations \citeeg{Vanderlinde2010, Sehgal2011}, optical richness \citeeg{Abell1958, Rykoff2012} or weak lensing (WL; \eg\ \citealt{Rozo2010}) as examples, which provide a ``true'' mass. This directly calibrates the observable--mass relation which is then applied to a much larger sample. The complications lie in that the ``true'' masses are, in fact, estimations, and the methods used to recover these cluster masses are subject to their own limitations. X-ray based cluster masses assume hydrostatic equilibrium \citeeg{Mantz2015} which may only be valid for a very small number and range of cluster masses. The Sunyaev--Zel'dovich Effect (SZE; \citealt{Sunyaev1972}), which uses the up--scattering of CMB photons to estimate cluster masses, provides accurate estimations of mass, but the ability to detect low mass galaxy clusters is currently limited by technology \citeeg{Carlstrom2002a}. WL estimates are, in principle, correct in the mean, but they suffer from signal-to-noise requirements, limiting their usefulness in low mass clusters, and potentially suffer from line-of-sight effects as WL is sensitive to all mass along the line-of-sight. Virial mass estimators which determine the cluster mass based on the motions of the member galaxies \citeeg{Ruel2014, Sifon2015} are promising in that it is a direct measurement of the depth of clusters potential well, but suffers from systematics due to cluster formation physics which disrupts the velocity field.

@@

While a large portion of the $\sim10^6$ interloping [\ion{O}{ii}] galaxies will be field (not associated with a bound structure) galaxies, the large area covered by HETDEX is expected to contain as many as 50 Virgo-sized ($M_{dyn}>10^{15}$ \msol) clusters at $z<0.5$. The near-complete spectroscopic coverage allows an unprecedentedly detailed look at a very large number of clusters ranging from group scales to the very massive. In addition to the recovery of accurate dynamical masses, detailed investigations of the of dynamical state of the clusters is possible.

Connecting the dynamical properties derived from spectroscopy to the properties inferred from other studies insures the greatest impact on future work. HETDEX overlaps with the Sloan Digital Sky Survey (SDSS; \citealt{Blanton2001a}), SDSS stripe 82 \citep{Annis2014}, DES, the \emph{Spitzer}/HETDEX Exploratory Large-Area Survey (SHELA; \citealt{Papovich2016}), and the \emph{Spitzer} IRAC Equatorial Survey (SpIES; Timlin \etal\ 2016, ApJ, submitted). While the potential dataset is very rich, two large issues remain.

@@

This work plans to address these concerns in the following ways. We create and evaluate a HETDEX like selection ``function'' of galaxies over a similarly large portion of the sky and use well adopted techniques to recover the dynamical properties, such as velocity dispersion and cluster mass. We compare these results to a series of targeted galaxy cluster observations, where each member galaxy is assumed to be observed. Each of these observations use realistic uncertainties from galaxy magnitude and line-flux limits. These strategies will better allow future work to predict the number and types of galaxy clusters which should be observed with VIRUS during both the HETDEX survey portion and through targeted follow up observations.

@@

\section{Data and Mock Observations}\label{sec:Data}
In this section, we describe the data products and the techniques used to replicate the HETDEX survey. We use the information from a large mock galaxy catalog supplemented by galaxies from the SDSS to create a realistic ``sky'' and ``observe'' it with a HETDEX-like observing strategy.

\subsection{The Buzzard Mock Catalogs}
\begin{figure*} 
	\includegraphics[width=\textwidth]{figures/oii_sdss.pdf} 
	\caption{\textit{Left}: CMD of 503113 $z<0.2$ galaxies take from the SDSS DR12 where the shading scales with the density of points. The two colored boxes show regions containing potential catalog galaxies. \textit{Right}: Probability histograms of the Log [\ion{O}{ii}] luminosity for the SDSS galaxies located in the two highlighted regions on the right. New [\ion{O}{ii}] luminosity (and subsequently fluxes) are assigned to catalog galaxies from slice sampling the probability histogram. See the text for a full description of the process.} \label{fig: oii sdss} 
\end{figure*}

The Buzzard mock galaxy catalogs (R. Wechsler et al., private communication) cover 398.49 \degsq\ between $4^h< RA < 6^h$ and $-61\degree < DEC < -41\degree$ and are derived from a combination of Sub-halo Abundance Matching (ShAM) and ADDSEDs (Adding Density Dependent Spectral Energy Distributions) tied to an in house n-body cosmological simulation. A brief description of the catalog creation is described as follows. The initial conditions are generated with a second-order Lagrangian perturbation theory using {\sc 2LPTic} \citep{Crocce2006}. Dark matter (DM) n-body simulations are run using {\sc LGadget-2} (a version of {\sc Gadget-2}; \citealt{Springel2005}). The DM halos are identified using the {\sc ROCKSTAR} halo finder \citep{Behroozi2013} which also calculates halo masses.

@@

\subsection{ {\rm[\ion{O}{ii}]} Luminosity}\label{sec: oii luminosity}
The Buzzard ``truth'' catalog does not provide [\ion{O}{ii}] luminosities so we must assign them empirically. We use 503113 galaxies from the SDSS Data Release 12 \citep{Alam2015} from $z = 0.05 - 0.2$, which are selected with no redshift warning, and place each galaxy on a color-magnitude diagram (CMD) of $M_r$ and $g-r$; see the left panel of Figure \ref{fig: oii sdss}.

To assign an [\ion{O}{ii}] luminosity to each galaxy in our catalog, we place the catalog galaxies on the same CMD and select all SDSS galaxies in a small 2D ($M_r$, $g-r$) bin around the galaxy. We extract all of the SDSS galaxies inside that bin and create a histogram of their [\ion{O}{ii}] luminosities, the right panel of Figure \ref{fig: oii sdss}. Using a slice sampling technique \citep{Neal1997} we assign the catalog galaxy an [\ion{O}{ii}] luminosity based on the distribution of SDSS galaxies extracted. For catalog galaxies which are placed on the CMD near no, or very few ($1\leq n<10$) galaxies we assign it zero [\ion{O}{ii}] luminosity or the mean luminosity, respectively. We find no evidence of a significant bias due to galaxies being assigned zero [\ion{O}{ii}] luminosity. For the galaxies in the Buzzard catalog, 1.3\% of the galaxies brighter than $\sdssg = 22$ mag (HETDEX's detection limit) have exactly zero [\ion{O}{ii}] luminosity. Of the 1.3\%, only 3.3\% (0.05\% of all galaxies) have $g-r < 1.5$.

The left panel of Figure~\ref{fig: oii sdss} shows the CMD of all SDSS galaxies. Two potential catalog galaxies are also placed on the CMD ($M_r, g-r = -17.7,~0.49$ and $M_r, g-r = -21.4,~1.24$) and indicated by the two colored boxes. The histograms show in the Figure's right panel show the probability density histograms of the Log [\ion{O}{ii}] luminosity for the SDSS galaxies in the 2D bin around the individual catalog galaxies. We sample the distribution and assign each catalog galaxy an [\ion{O}{ii}] luminosity which is then converted into a flux.

\subsection{Mock Observations}\label{sec: observations}
\begin{figure} 
	\includegraphics[width=\columnwidth]{figures/pointings.pdf} 
	\caption{Representative observation tiling scheme for the HETDEX $16' \times 16'$ pointings. Each colored square is a single VIRUS IFU and the dashed octagons approximate the size of a single observation. See the text for more details.} \label{fig: ifu layout} 
\end{figure}

HETDEX will perform blind spectroscopy (R $\sim$ 750 in $3500 - 5500~\AAA$) over two fields along the celestial equator. The 300 \degsq, spring field and 120 \degsq\ fall field will have no preselected targets. Using VIRUS on the 10-m Hobby-Eberly Telescope \citep{Ramsey1998} the completed survey is expected to have an overall fill-factor of 1/4.5, meaning that the entire area could be covered with 4.5 dithers of the entire survey.

@@

This means that when selecting galaxies from the Buzzard catalog we assume an observation for all galaxies laying within a colored, IFU square in Figure~\ref{fig: ifu layout}. Galaxies which lie between the IFUs are missed, as well as the galaxies which lie between the pointings, as there is no overlap between one pointing and the next. To cover the 398.49 \degsq\ field of the Buzzard catalog we require 5370 pointings where 0.015 \degsq\ of each pointing is covered by an IFU. The total area of the sky covered by an IFU is 80.80 \degsq\ which gives a filling factor of 1/4.65, slightly decreased from the expected filling factor of 1/4.5.

The spectral coverage allows for the detection of [\ion{O}{ii}] ($\lambda\lambda 3727,3729$) emitters to $z\sim 0.5$ and Ca H ($\lambda 3968.5$) and K ($\lambda 3933.7$) absorption features to $z\sim 0.4$. HETDEX is expected to detect sources with continuum brighter than $\sdssg=22$ mag, and emission line strengths above $3.5\times10^{-17}$ \ergscm.

In this work we consider two separate observing strategies, targeted and survey-like. The targeted observations use ``direct'' observations where each cluster is targeted individually, and every cluster member galaxy is assumed to be observed. The survey observations mimic the HETDEX observation pattern across the sky, where no cluster is directly targeted and not all cluster member galaxies are observed. Both of these observations have HETDEX-like galaxy detection thresholds, and for comparison we also include a set of targeted observations with ``perfect'' knowledge. Perfect observations assume no detection threshold, if a cluster member galaxy is observed, it is also detected. This provides an important best-case scenario, and differs from the true cluster properties because the cluster properties are still calculated. These observations provide three levels of quality with ``perfect knowledge'' being the highest and survey being the lowest.

\section{Recovery of Parameters}\label{sec:recovery}
 In the following sections, we outline the methods we use to derive the dynamical properties of the galaxy clusters in our sample. This is not meant to be an exhaustive study of the different methods used to recover these parameters. The following is, in many cases, a subset of the available methods to derive any single parameter. The specific choice of method may improve or diminish the accuracy of the recovered parameter, but the methods chosen were to facilitate comparison with other observational studies \citeeg{Boada2016a}.

@@

In simple terms, the cluster redshift is the mean of the redshifts of all galaxies associated with the cluster. For this work we rely on the biweight location estimator \citep{Beers1990} because it is resistant to outlying galaxies. Although this work assumes that we know each galaxy's redshift to infinite precision, in practice, we find a simple weighted mean provides a reliable estimate of $z_c$ when there are uncertainties on the individual galaxy redshifts.

\subsection{Line-of-Sight Velocity Dispersion}\label{sec: LOSVD}
We first calculate the LOSV to each galaxy, where
\begin{equation}
	LOSV = c\frac{z - z_c}{1+z_c}
\end{equation}
and $c$ is the speed of light in \kms, $z$ is the redshift of the individual galaxy, and $z_c$ is the overall cluster redshift described in the previous section.

The line-of-sight velocity dispersion (LOSVD) is calculated using a method of maximum likelihood following \cite{Walker2006}. We maximize the probability function 
\begin{equation}\label{eq: jointGaussian}
p(\{v_1, ..., v_N\})=\displaystyle\prod_{i=1}^{N}\frac{1}{\sqrt{2\pi(\sigma_i^2+\sigma_p^2)}}\exp\biggl[-\frac{1}{2}\frac{(v_i-\langle u \rangle)^2}{(\sigma_i^2+\sigma_p^2)}\biggr]
\end{equation}
where $\sigma_p$, $\langle\mu\rangle$, and $\sigma_i$ is the LOSVD, the average radial velocity and the error on the individual LOSVs respectively, using a Monte Carlo Markov Chain (MCMC) sampler ({\sc emcee}\footnote{\url{http://dan.iel.fm/emcee/current/}}; \citealt{Foreman-Mackey2013}) which is based on affine-invariant ensemble sampler (see \citealt{Goodman2010} for details on affine-invariant samplers). We draw twenty thousand samples from the posterior probability distribution using simple priors, $\langle\mu\rangle$ lies between the maximum and minimum LOSV and $0< \sigma_p < 1400$ \kms. When the full distribution of LOSVDs is not used, the final LOSVD is quoted as the median value of the posterior probability distribution with 68\% error bars defined as the 16th and 84th percentiles of the same distribution.

In principle, a single statistic such as the biweight scale estimator or the gapper estimator (both from \citealt{Beers1990}) with many bootstrap resamplings could be used to construct a distribution of $\sigma_p$. In simple tests where the values of both $\sigma_p$ and $\langle\mu\rangle$ are known. The 68\% error bars derived from the MCMC method give slightly better results with the true LOSVD value bracketed by the error bars in $\sim68\%$ of the cases versus $\sim57\%$ with bootstrapping and a single statistic. In addition, we prefer the maximum likelihood method for its straight forward treatment of the errors in the LOSV measurements, which will become important in future observations of real clusters \citeeg{Boada2016a}.

\subsection{Dynamical Mass from Scaling Relations}\label{sec: mass}
The relationship between the LOSVD and cluster dynamical mass has been the focus of several studies \citeeg{Evrard2008, Saro2013, Sifon2013, VanderBurg2014}, and a best fitting relationship for the mass enclosed by $r_{200c}$ of the form
\begin{equation}\label{eq:power law}
	M_{200c} = \frac{10^{15}}{h(z)} \bigg{(}\frac{\sigma_{1D}}{A_{1D}} \bigg{)}^{1/\alpha} \Msol
\end{equation}
with $A_{1D} = 1177 \pm 4.2$ \kms\ (\citealt{Munari2013}; referred to as $\sigma_{15}$ in \citealt{Evrard2008} and other works), $\alpha = 1/3$, $h(z) = H(z)/100$, and $\sigma_{1D}$ is the LOSVD of the velocity tracers (dark matter particles, subhalos or galaxies). $H(z) = H_0 E(z)$ and $E(z) = \sqrt{\Omega_m(1+z^3)+\Omega_{\Lambda}}$.

>>>>

%%%%% AUTHORS - PLACE YOUR OWN PACKAGES HERE %%%%%
%\usepackage{epsf}
\usepackage{color}
\usepackage{graphicx}
\usepackage{amsmath}	% Advanced maths commands
\usepackage{amssymb}	% Extra maths symbols
\usepackage{mathrsfs}	% Extra extra math symbols
\usepackage{natbib}
%\usepackage[colorlinks,urlcolor=blue,citecolor=blue,linkcolor=blue]{hyperref}
\usepackage{multirow}
\usepackage{etoolbox}

@@

\begin{abstract}
\noindent
The distribution of massive clusters of galaxies depends strongly on the total cosmic mass density, the mass variance, and the dark energy equation of state. As such, measures of galaxy clusters can provide constraints on these parameters and even test models of gravity, but only if observables of clusters can lead to accurate estimates of their total masses. Here, we carry out a study to investigate the ability of a blind spectroscopic survey to recover accurate galaxy cluster masses through their velocity dispersion. We focus on the Hobby Eberly Telescope Dark Energy Experiment (HETDEX), which will employ the new VIRUS integral field unit (IFU) spectrograph, over 420 \degsq\ on the sky with a 1/4.5 fill factor. The instrument covers the blue/optical portion of the spectrum (3500--5500~\AAA), allowing surveys with VIRUS to measure redshifts for a large sample of galaxies out to $z < 0.5$ based on their absorption features or [\ion{O}{ii}] $\lambda$3727 emission (and Lyman-$\alpha$ over $1.9 < z < 3.5$). We use a detailed mock galaxy catalog from a semi-analytic model to simulate surveys observed with VIRUS, including: (1) a blind, HETDEX-like survey with an incomplete but uniform spectroscopic selection function; and (2) IFU surveys that target clusters directly, obtaining spectra of all galaxies in a VIRUS-sized field. For both surveys, we include realistic uncertainties from galaxy magnitude and line-flux limits. We benchmark both surveys against spectroscopic observations with ``perfect" knowledge of galaxy line-of-sight velocities. Using both observing strategies, we produce cluster mass probability density functions $P(M_{200c}|\vec{x})$ of a cluster mass ($M_{200c}$) as a function of an observable parameter or set of observable parameters, $\vec{x}$, where we consider cases of where $\vec{x} = \{\sigma\}$, $=\{\sigma, z\}$, and $=\{\sigma,z, N_{gal}\}$ for velocity dispersion, $\sigma$, redshift, and number of observed galaxies, $N_{gal}$. \editorial{This sentence will summarize how well HETDEX will do, and how that might be improved with Targeted observations.}
\end{abstract}

\section{Introduction}\label{sec: Introduction}
Our ability to perform precision cosmology with clusters of galaxies has reached a critical point. The widely accepted $\Lambda$CDM model of cosmology makes explicit predictions about the mass function of galaxy clusters in the universe. Measuring this mass function across many redshifts, in turn, provides constraints on the cosmology. Today, large-area sky surveys are providing observations of large numbers of clusters, but systematics in deriving cluster masses dominate the error budget \citeeg{Sehgal2011,Plank2014, Bocquet2015}. To place further constraints on the $\Lambda$CDM model of cosmology, we must decrease these systematics.

As mass is not a direct observable, a lot of work is underway to characterize galaxy cluster masses with an observable feature of galaxy clusters. The goal is to constrain, as best possible, $P(M|z, \vec{x})$ the probability ($P$) that a galaxy cluster of given mass ($M$), located at redshift ($z$) determined using an observable parameter or parameters ($\vec{x}$). Generally, cluster mass calibrations fall into two distinct camps, simulation based and direct or statistical calibration.

@@

The second broad camp is the direct calibration of cluster masses. This recipe has two distinct but not always independent tracks. The ``direct'' method uses direct observations of a small set of clusters and then uses known mass estimators, including X-ray temperatures and luminosities \citeeg{Mantz2010, Rykoff2014}, cosmic microwave background (CMB) observations \citeeg{Vanderlinde2010, Sehgal2011}, optical richness \citeeg{Abell1958, Rykoff2012} or weak lensing (WL; \eg\ \citealt{Rozo2010}) as examples, which provide a ``true'' mass. This directly calibrates the observable--mass relation which is then applied to a much larger sample. The complications lie in that the ``true'' masses are, in fact, estimations, and the methods used to recover these cluster masses are subject to their own limitations. X-ray based cluster masses assume hydrostatic equilibrium \citeeg{Mantz2015} which may only be valid for a very small number and range of cluster masses. The Sunyaev-Zel'dovich Effect (SZE; \citealt{Sunyaev1972}), which uses the up-scattering of CMB photons to estimate cluster masses, provides accurate estimations of mass, but the ability to detect low mass galaxy clusters is currently limited by technology \citeeg{Carlstrom2002a}. WL estimates are, in principle, correct in the mean, but they suffer from signal-to-noise requirements, limiting their usefulness in low mass clusters, and potentially suffer from line-of-sight effects as WL is sensitive to all mass along the line-of-sight. Virial mass estimators which determine the cluster mass based on the motions of the member galaxies \citeeg{Ruel2014, Sifon2015} are promising in that it is a direct measurement of the depth of clusters potential well, but suffer from systematics due to cluster formation physics which disrupts the velocity field.

@@

While a large portion of the $\sim10^6$ interloping lower redshift galaxies will be field (not associated with a bound structure) galaxies, the large area covered by HETDEX is expected to contain as many as 50 Virgo-sized (halo mass $>10^{15}$ \msol) clusters at $z<0.5$. The near-complete spectroscopic coverage allows an unprecedentedly detailed look at a very large number of clusters ranging from group scales to the very massive. In addition to the recovery of accurate dynamical masses, detailed investigations of the of dynamical state of the clusters is possible.

@@

This work plans to address these concerns in the following ways. We create and evaluate a HETDEX like selection ``function'' of galaxies over a similarly large portion of the sky and use well adopted techniques to recover the dynamical properties, such as velocity dispersion and cluster mass. In addition to standard techniques of cluster mass estimation, we investigate probability based and machine learning based approaches of cluster mass prediction. We compare these results to a series of targeted galaxy cluster observations, where each member galaxy is assumed to be observed. Each of these observations use realistic uncertainties from galaxy magnitude and line-flux limits. These strategies will better allow future work to predict the number and types of galaxy clusters which should be observed with VIRUS during both the HETDEX survey portion and through targeted follow up observations.

@@

\section{Data and Mock Observations}\label{sec:Data}
In this section, we describe the data products and the techniques used to replicate the HETDEX survey. We use the information from a large mock galaxy catalog enhanced by the emission line properties of galaxies in the SDSS to create a realistic ``sky'' and ``observe'' it with a HETDEX-like observing strategy.

\subsection{The Buzzard Mock Catalogs}
\begin{figure*} 
	\includegraphics[width=\textwidth]{figures/oii_sdss.pdf} 
	\caption{\textit{Left}: CMD of 503113 $z<0.2$ galaxies take from the SDSS DR12 where the shading scales with the density of points. The two colored boxes show regions containing potential catalog galaxies. \textit{Right}: Probability histograms of the Log [\ion{O}{ii}] luminosity for the SDSS galaxies located in the two highlighted regions on the right. The [\ion{O}{ii}] luminosities are assigned to catalog galaxies from slice sampling the probability histogram and converted to fluxes using the redshift of each galaxy.} \label{fig: oii sdss} 
\end{figure*}

The Buzzard mock galaxy catalogs cover 398.49 \degsq\ between $4^h< RA < 6^h$ and $-61\degree < DEC < -41\degree$ and are derived from a combination of Sub-halo Abundance Matching (ShAM) and ADDSEDs (Adding Density Dependent Spectral Energy Distributions) tied to an in house n-body cosmological simulation. A brief description of the catalog creation is described as follows. The initial conditions are generated with a second-order Lagrangian perturbation theory using {\sc 2LPTic} \citep{Crocce2006}. Dark matter (DM) n-body simulations are run using {\sc LGadget-2} (a version of {\sc Gadget-2}; \citealt{Springel2005}). The DM halos are identified using the {\sc ROCKSTAR} halo finder \citep{Behroozi2013} which also calculates halo masses.

@@

\subsection{Conditional [\ion{O}{ii}] Flux Probability Distribution Functions}\label{sec: oii luminosity}
We use the SDSS DR12 \citep{Alam2015} catalogs to assign [\ion{O}{ii}] emission line strengths to the galaxies in the Buzzard catalog. We use 503113 galaxies from $z = 0.05 - 0.2$, which are selected with no redshift warning, and place each galaxy on a color-magnitude diagram (CMD) of $M_r$ and $g-r$; see the left panel of Figure \ref{fig: oii sdss}.

To assign an [\ion{O}{ii}] luminosity to each galaxy in our catalog, we place the catalog galaxies on the same CMD and select all SDSS galaxies in a small 2D ($M_r$, $g-r$) bin around the galaxy. We extract all of the SDSS galaxies inside that bin and create a histogram of their [\ion{O}{ii}] luminosities, the right panel of Figure \ref{fig: oii sdss}. Using a slice sampling technique \citep{Neal1997} we assign the catalog galaxy an [\ion{O}{ii}] luminosity based on the distribution of SDSS galaxies in that bin. In very few cases (1.3\% of galaxies) do the $g-r$ and $M_r$ magnitudes of the galaxies in the Buzzard catalog not overlap with the distributions in SDSS. For these objects, we assign them zero [\ion{O}{ii}] flux, but this has no impact on our analysis. For catalog galaxies with have very few ($1\leq N<10$) SDSS galaxies in their respective bin, we assign it the mean [\ion{O}{ii}] flux.

Figure~\ref{fig: oii sdss} illustrates this process. The numbered boxes in the left panel show two bins ($M_r, g-r = -17.7,~0.49$ and $M_r, g-r = -21.4,~1.24$) in the CMD of $0.05 < z < 0.2$ SDSS galaxies. The right panel shows the Log [\ion{O}{ii}] luminosity distribution functions, $p($[\ion{O}{ii}]$| M_r, g-r)$, which we use to assign [\ion{O}{ii}] luminosity to each object. The luminosity is then converted into an [\ion{O}{ii}] flux through 
\begin{equation}
	F = \frac{L}{4\pi D_L}
\end{equation}
where $D_L$ is the luminosity distance \citeeg{Hogg2010}.

\subsection{HETDEX}\label{sec: hetdex}
\begin{figure} 
	\includegraphics[width=\columnwidth]{figures/pointings.pdf} 
	\caption{Representative observation tiling scheme for the HETDEX $16' \times 16'$ pointings. Each colored square is a single VIRUS IFU and the dashed octagons approximate the size of a single observation. See the text for more details.} \label{fig: ifu layout} 
\end{figure}

\editorial{There are quite a few words copied from Casey's SHELA paper.}
HETDEX will perform a blind survey which will measure the redshifts of $8 \times \sim 10^5$ Ly$\alpha$ emitting galaxies (LAEs) between $1.9 < z < 3.5$ using a collection of 78 wide-field IFUs spectrographs covering the wavelength region $3500 - 5500$~\AAA\ at R $\sim$ 750 \citep{Hill2008}. The goal of these observations will be to provide sub-percent level measurements of the Hubble expansion parameter and the angular diameter distance at $z \sim 2$ via the large scale distribution of galaxies in the redshift range of HETDEX. The result will be a significant constraint on the evolution of dark energy that is competitive with (and independent of) values based on surveys of the Ly$\alpha$ forest.

The entire HETDEX survey will cover 420 \degsq\ with a 1/4.5 filling factor over two fields: a $\sim 300$ \degsq\ northern field, and a $\sim 140$ \degsq\ equatorial region. The $10 \sigma$ detection limit for these spectra will be $3.5\times10^{-17}$ \ergscm\ at 5000 \AAA, or equivalently for continuum objects, $g = 21.9$ mag. The spectral coverage allows for the detection of [\ion{O}{ii}] ($\lambda\lambda 3727,3729$) emitters to $z\sim 0.5$ and Ca H ($\lambda 3968.5$) and K ($\lambda 3933.7$) absorption features to $z\sim 0.4$.

@@

\subsection{Mock Observations}\label{sec: observations}
This means that when selecting galaxies from the Buzzard catalog we assume an observation for all galaxies laying within a colored, IFU square in Figure~\ref{fig: ifu layout}. Galaxies which lie between the IFUs are missed, as well as the galaxies which lie between the pointings, as there is no overlap between one pointing and the next. To cover the 398.49 \degsq\ field of the Buzzard catalog we require 5370 pointings where 0.015 \degsq\ of each pointing is covered by an IFU. The total area of the sky covered by an IFU is 80.80 \degsq\ which gives a filling factor of 1/4.65, slightly decreased from the expected filling factor of 1/4.5.

In this work we consider two separate observing strategies, Targeted and Survey-like. The Targeted observations use ``direct'' observations where each cluster is targeted individually, and every cluster member galaxy is assumed to be observed. The Survey observations mimic the HETDEX observation pattern across the sky, where no cluster is directly targeted and not all cluster member galaxies are observed. Both of these observations have HETDEX-like galaxy detection thresholds, and for comparison we also include a set of Targeted observations with ``perfect'' knowledge. Perfect observations assume no detection threshold, if a cluster member galaxy is observed, it is also detected. This provides an important best-case scenario, and differs from the true cluster properties because the cluster properties are still calculated. These observations provide three levels of quality with ``Perfect knowledge'' being the highest and Survey being the lowest.

\section{Recovery of Parameters}\label{sec:recovery}
In the following subsections, we outline the methods we use to derive the dynamical properties of the galaxy clusters in our sample. The following is, in many cases, a subset of the available methods to derive any single parameter. The specific choice of method may improve or diminish the accuracy of the recovered parameter, but the methods chosen were to facilitate comparison with other observational studies \citeeg{Boada2016a}.

@@

In simple terms, the cluster redshift is the mean of the redshifts of all galaxies associated with the cluster, where the mean is the first moment of the velocity (redshift) distribution function $p(z)$. In practice, the first moment is strongly subject to outliers, so we rely instead on the biweight location estimator \citep{Beers1990} through\footnote{Implemented as part of the {\sc astLib} Python library. See \hbox{\url{http://astlib.sourceforge.net}}}:
\begin{equation}
C_{BI} = M + \frac{\sum_{|u_i| < 1} (x_i - M)(1-u_i^2)^2}{\sum_{|u_i| < 1}(1-u_i^2)^2}
\end{equation}
where $x_i$ are the individual redshifts, $M$ is the median redshift and $u_i$ is given by:
\begin{equation}
	u_i = \frac{(x_i - M)}{c\mathrm{MAD}}
\end{equation}.
MAD is the median absolute deviation, also defined in \cite{Beers1990}, and $c$ is the a tuning constant. We choose $c=6$ (the suggested value) which balances computational speed and location accuracy.

Although this work assumes that we know each galaxy's redshift to infinite precision, in practice, we find a simple weighted mean provides a reliable estimate of $z_c$ when there are uncertainties on the individual galaxy redshifts.

\subsection{Line-of-Sight Velocity Dispersion}\label{sec: LOSVD}
We calculate the LOSV to each galaxy, where
\begin{equation}
	\mathrm{LOSV} = c\frac{z - z_c}{1+z_c}
\end{equation}
and $c$ is the speed of light in \kms, $z$ is the redshift of the individual galaxy, and $z_c$ is the overall cluster redshift described in the previous section.

We follow the maximum likelihood method of \cite{Walk2006} to estimate the line-of-sight velocity dispersion (LOSVD). We maximize the probability function 
\begin{equation}\label{eq: jointGaussian}
p(\{v_1, ..., v_N\})=\displaystyle\prod_{i=1}^{N}\frac{1}{\sqrt{2\pi(\sigma_i^2+\sigma_p^2)}}\exp\biggl[-\frac{1}{2}\frac{(v_i-\langle u \rangle)^2}{(\sigma_i^2+\sigma_p^2)}\biggr]
\end{equation}
where $\sigma_p$, $\langle\mu\rangle$, and $\sigma_i$ is the LOSVD, the average radial velocity and the error on the individual LOSVs respectively, using a Monte Carlo Markov Chain (MCMC) sampler ({\sc emcee}\footnote{\url{http://dan.iel.fm/emcee/current/}}; \citealt{Foreman-Mackey2013}) which is based on affine-invariant ensemble sampler (see \citealt{Goodman2010} for details on affine-invariant samplers). We draw twenty thousand samples from the posterior probability distribution using simple priors, $\langle\mu\rangle$ lies between the maximum and minimum LOSV and $0< \sigma_p < 1400$ \kms. We set the upper limit on the LOSVD as the LOSVD corresponding to a $10^{16}$ \Msol\ cluster at $z\sim0.0$, higher mass than any expected cluster. When the full distribution of LOSVDs is not used, the final LOSVD is quoted as the median value of the posterior probability distribution with 68\% error bars defined as the 16th and 84th percentiles of the same distribution.

In principle, a single statistic such as the biweight scale estimator or the gapper estimator (both from \citealt{Beers1990}) with many bootstrap resamplings could be used to construct a distribution of $\sigma_p$. In simple tests where the values of both $\sigma_p$ and $\langle\mu\rangle$ are known, the 68\% error bars derived from the MCMC method give slightly better results with the true LOSVD value bracketed by the error bars in $\sim68\%$ of the cases versus $\sim57\%$ with bootstrapping and a single statistic. In addition, we prefer the maximum likelihood method for its straight forward treatment of the errors in the LOSV measurements, which will become important in the practical application to real data \citeeg{Boada2016a}.

\subsection{Estimates of Cluster Mass}\label{sec: mass}
\subsubsection{Power Law Based Method}
The relationship between the LOSVD and cluster dynamical mass has been the focus of several many \citeeg{Evrard2008, Saro2013, Sifon2013, VanderBurg2014}, where the relationship for the mass enclosed by $r_{200c}$ takes the form
\begin{equation}\label{eq:power law}
	M_{200c} = \frac{10^{15}}{h(z)} \bigg{(}\frac{\sigma_{1D}}{A_{1D}} \bigg{)}^{1/\alpha} \Msol
\end{equation}
with $A_{1D} = 1177 \pm 4.2$ \kms\ (\citealt{Munari2013}; referred to as $\sigma_{15}$ in \citealt{Evrard2008} and other works), $\alpha = 1/3$, $h(z) = H(z)/100$, and $\sigma_{1D}$ is the LOSVD of the velocity tracers (dark matter particles, subhalos or galaxies). $H(z) = H_0 E(z)$ and $E(z) = \sqrt{\Omega_m(1+z^3)+\Omega_{\Lambda}}$.

A growing body of work suggests that there is a significant difference in the observed LOSVD depending on the velocity tracers used. Specifically, while there is little difference between using galaxies and their host DM subhalos, there is a significant over estimation of the LOSVD when using galaxies/subhalos compared to DM particles \citep{Munari2013}. We follow other works \citeeg{Kirk2015, Sifon2015a} using the scaling relation, given in Equation~\ref{eq:power law} from \cite{Munari2013} to facilitate comparisons with other observational studies, which rely on galaxies as tracers.
